Joint Satellite Distributions in the Local Group

### 2017-09-27 paper/paper.tex
+1 paragraph on results

>>>>

We compare the two satellite distributions by always keeping the same
number of satellites around each galaxy.
This means that the magnitude cut corresponding to the faintest
satellite included in the sample is different in each case.
We make this choice for two reasons. 
First to always be sure that there is a non-zero number of satellites to make the computations. 
Second, to be able to compare the two halos at a fixed number of
satellites.

We test the shape and alignment statistics for 11 up 25 satellites.
The lowest number corresponds to the number of classical Milky Way
satellites.
We compare the resuls of the satellite distributions with the average
of from 10000 randomized version of the same satellites.
The spherical randomization is done as described in Section X.

Figure \ref{fig:general} summarized the results. 
The left column shows
